Naturalness in U(1) extensions of the MSSM

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Added stop fine tuning plot into draft

To illustrate this, in Fig. \ref{} we show the variation in fine
tuning when we fix $\mu=-97$ GeV and $B=-85$ GeV, and scan over the
stop masses and mixing, with $500 \textrm{ GeV} \leq
m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq
A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.
However this tuning only really becomes large for very large stop
masses.  On the other hand if the cuttoff is increased then stop masses of
several TeV can result in tuning of [insert] as shown in
Fig.~\ref{}.\\ \\

>>>>

\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{mssm_stop_tuning.png}}
\caption{Scatter plot of fine tuning in the MSSM as a function of
the lightest stop mass, $m_{\tilde{t}_1}$ for the cut-off scales (from 
bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
\label{Fig:mssmstoptuning}
\end{center}
\end{figure}
To illustrate this, in Fig.~\ref{Fig:mssmstoptuning} we show the variation in fine
tuning when we fix $\mu=-97$ GeV and $B=-85$ GeV, and scan over the
stop masses and mixing, with $500 \textrm{ GeV} \leq
m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq
A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.
However this tuning only really becomes large for very large stop
masses.  On the other hand if the cuttoff is increased then stop masses of
several TeV can result in tuning of [insert] as shown in
Fig.~\ref{}.\\ \\
